---
title: "Superhero Knowledge & Preferences Survey"
survey-settings:
  show-previous: true
  auto-scroll: false
  rate-survey: false
  all-required: false
  required:
    - consent
    - age_group
    - universe_pref
    - fav_hero
    - hero_qualities
barcolor: "#5654A2"
barposition: "top"
theme: "default"
footer: "Superhero Survey · Powered by surveydown"
---

```{r}
#| context: setup
#| echo: false
library(surveydown)
```

--- welcome

## Welcome to the Superhero Survey! 🦸

We're collecting data on superhero knowledge and preferences. This short survey takes about **3–5 minutes** to complete. Your responses are anonymous.

```{r}
#| echo: false
sd_question(
  type  = "mc",
  id    = "consent",
  label = "Do you consent to participate in this survey?",
  option = c(
    "Yes, I consent" = "yes",
    "No, I do not consent" = "no"
  )
)
```

`r sd_nav(label_next = "Start Survey →")`

--- screener

## A Quick Check

```{r}
#| echo: false
sd_question(
  type  = "mc",
  id    = "age_group",
  label = "What is your age group?",
  option = c(
    "Under 18" = "under18",
    "18–24"    = "18_24",
    "25–34"    = "25_34",
    "35–44"    = "35_44",
    "45–54"    = "45_54",
    "55+"      = "55plus"
  )
)
```

```{r}
#| echo: false
sd_question(
  type  = "mc",
  id    = "superhero_fan",
  label = "How would you describe yourself as a superhero fan?",
  option = c(
    "Hardcore fan — I know my lore!"       = "hardcore",
    "Casual fan — I enjoy the movies/shows" = "casual",
    "Not really a fan"                      = "not_fan"
  )
)
```

`r sd_nav()`

--- knowledge

## Superhero Knowledge

```{r}
#| echo: false
sd_question(
  type  = "mc",
  id    = "universe_pref",
  label = "Which superhero universe are you more familiar with?",
  option = c(
    "Marvel (MCU)"       = "marvel",
    "DC (DCU)"           = "dc",
    "Both equally"       = "both",
    "Neither — I'm new!" = "neither"
  )
)
```

```{r}
#| echo: false
sd_question(
  type  = "slider_numeric",
  id    = "knowledge_score",
  label = "How would you rate your overall superhero knowledge? (0 = none, 10 = expert)",
  option = 0:10,
  default = 5
)
```

```{r}
#| echo: false
sd_question(
  type  = "mc_multiple",
  id    = "media_consumed",
  label = "Which superhero media have you consumed? (Select all that apply)",
  option = c(
    "Marvel movies (MCU)"          = "mcu_movies",
    "DC movies (DCU)"              = "dcu_movies",
    "Animated series (e.g., X-Men, Batman TAS)" = "animated",
    "Comic books"                  = "comics",
    "Video games"                  = "games",
    "TV shows (e.g., Daredevil, The Flash)" = "tv_shows",
    "None of the above"            = "none"
  )
)
```

`r sd_nav()`

--- trivia

## Quick Trivia

```{r}
#| echo: false
sd_question(
  type  = "mc",
  id    = "spiderman_q",
  label = "What radioactive creature gave Spider-Man his powers?",
  option = c(
    "Spider"      = "spider",
    "Scorpion"    = "scorpion",
    "Wasp"        = "wasp",
    "Radioactive Man" = "rad_man"
  )
)
```

```{r}
#| echo: false
sd_question(
  type  = "mc",
  id    = "batman_q",
  label = "Which of these is NOT one of Batman's well-known villains?",
  option = c(
    "The Joker"    = "joker",
    "Lex Luthor"   = "lex",
    "Two-Face"     = "two_face",
    "The Riddler"  = "riddler"
  )
)
```

```{r}
#| echo: false
sd_question(
  type  = "mc",
  id    = "avengers_q",
  label = "Who was the first Avenger, according to the MCU?",
  option = c(
    "Iron Man"     = "iron_man",
    "Captain America" = "cap",
    "Thor"         = "thor",
    "Nick Fury"    = "fury"
  )
)
```

`r sd_nav()`

--- preferences

## Your Preferences

```{r}
#| echo: false
sd_question(
  type  = "text",
  id    = "fav_hero",
  label = "Who is your all-time favorite superhero?",
  placeholder = "e.g., Spider-Man, Wonder Woman, Black Panther..."
)
```

```{r}
#| echo: false
sd_question(
  type  = "mc_multiple_buttons",
  id    = "hero_qualities",
  label = "What qualities do you value most in a superhero? (Select up to 3)",
  option = c(
    "Courage"        = "courage",
    "Intelligence"   = "intelligence",
    "Humor"          = "humor",
    "Moral compass"  = "morality",
    "Raw power"      = "power",
    "Relatability"   = "relatable",
    "Sacrifice"      = "sacrifice"
  )
)
```

```{r}
#| echo: false
sd_question(
  type  = "mc",
  id    = "power_choice",
  label = "If you could have one superpower, what would it be?",
  option = c(
    "Flight"           = "flight",
    "Super strength"   = "strength",
    "Telepathy"        = "telepathy",
    "Time manipulation" = "time",
    "Invisibility"     = "invisibility",
    "Healing factor"   = "healing"
  )
)
```

```{r}
#| echo: false
sd_question(
  type  = "slider",
  id    = "hero_vs_villain",
  label = "Where do you fall on the hero–villain spectrum?",
  option = c(
    "Pure hero"       = "hero",
    "Mostly heroic"   = "mostly_hero",
    "Anti-hero"       = "antihero",
    "Morally grey"    = "grey",
    "Villain with reasons" = "villain_reasons",
    "Pure villain"    = "villain"
  )
)
```

`r sd_nav()`

--- followup

## A Bit More...

```{r}
#| echo: false
sd_question(
  type  = "mc",
  id    = "team_solo",
  label = "Do you prefer heroes who work alone or as part of a team?",
  option = c(
    "Lone wolf"          = "solo",
    "Team player"        = "team",
    "Depends on the hero" = "depends"
  )
)
```

```{r}
#| echo: false
sd_question(
  type  = "mc",
  id    = "origin_pref",
  label = "Which hero origin story do you find most compelling?",
  option = c(
    "Accident / scientific mishap (e.g., Hulk, Spider-Man)" = "accident",
    "Chosen / destined (e.g., Thor, Captain Marvel)"        = "destined",
    "Self-made through training/tech (e.g., Batman, Iron Man)" = "self_made",
    "Born with powers (e.g., Superman, Storm)"              = "born"
  )
)
```

```{r}
#| echo: false
sd_question(
  type  = "textarea",
  id    = "hero_design",
  label = "If you could design your own superhero, describe them in a few sentences:",
  placeholder = "Powers, backstory, costume — let your imagination run wild!",
  height = "120px"
)
```

`r sd_nav()`

--- final

## Almost Done!

```{r}
#| echo: false
sd_question(
  type  = "mc",
  id    = "recommend",
  label = "Would you recommend this survey to a fellow superhero fan?",
  option = c(
    "Absolutely!"      = "yes",
    "Maybe"            = "maybe",
    "Probably not"     = "no"
  )
)
```

```{r}
#| echo: false
sd_question(
  type  = "textarea",
  id    = "comments",
  label = "Any other thoughts on superheroes or this survey? (Optional)",
  placeholder = "Feel free to share anything...",
  height = "100px"
)
```

### Thank you for completing the survey! 🦸‍♀️🦸‍♂️

Your responses help us understand what makes superheroes so beloved. You're a true hero for participating!

`r sd_close(label_close = "Exit Survey")`
